Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-08-07 volunteer-clouds-ieee-ci-si.tex

\subsection{{\sf NodIO-W$^2$}, a WebWorker-based architecture}

>>>>

\subsection{{\sf NodIO-W$^2$}, a Web Worker-based architecture}

Javascript has commonly been used to develop client-side scripts that handle the interaction 
with the user, communicate asynchronously with servers and update the content that is displayed \cite{flanagan2006javascript}.
Long-running scripts like those proposed in this work can interfere with the responsiveness of 
the page. The Web Workers specification \cite{hickson2012web} defines an API that allows Web developers 
to execute scripts in parallel with user interaction scripts of the main page. 
Worker scripts are spawned in the background allowing a thread-like operation with 
message-passing as the coordination mechanism.
